The fundamental shape of dynamic experiences is preserved in episodic memory

### 2018-07-13 main.tex
fixed some typos

\subsubsection{Modeling verbal recall}
After watching the video, participants verbally recalled (in order) as much of the episode as they could.  We used the same topic model (fit with the text descriptions of the video) to transform participants' verbal recall transcripts. The result was a sentences (range: 68 to 294, mean: 131.94) by topics (100) matrix for each participant, where each row represents a probabalistic mixture of topics for a given window of sentences during recall. An example participant's (#13) recall model is plotted in Fig.~\ref{fig:model}c. Like the video model, topic vectors were sparse and changed gradually.  Note that the topics were derived solely from the text descriptions of the video, and so the topic models estimated for recall are dependent on the topics present in the video. This approach effectively projects the participants' verbal recall into the video's `topic space'', allowing us to directly compare them to the video model.

@@

\begin{figure}[t!]
\centering
\includegraphics[width=1\textwidth]{figs/4_trajectory.pdf}
\caption{\small \textbf{Video and recall trajectory plots.} A). 2-dimensional embedding of the video events model. The arrows indicate the forward direction of the video events. B). 2-dimensional embedding of the average recall events model.  The colors refer to the most similar video events. The directional lines connecting the points represent the true video event order. The arrows represent the average direction of all recall event transitions (i.e. a line segment connecting two consecutive recall event vectors) that intersected a box (width=.25) centered on the origin of the arrow.
\label{fig:trajectory}
\end{figure}

@@

\subsubsection{Topic vector word clouds}
 We created word clouds to visualize the themes contained in the ``hinge-point'' recall events of the model. One component of the topic model comprises a words (???) by topics (100) matrix (R), where the rows represent the weighting of a given word on each topic. Each event (video and recall) was associated with a 1 by 100 topic vector (v) representing the mixture of topics contained in the event. To find words associated with a given event, we computed the dot product between R and v, which gave a 1 by # of words vector where the values represent the `activation' of each of in the event. We normalized these vectors by subtracting the average `activation' across all events. We performed this analysis for each of the line segment model `hinge-points' (i.e. the average recall events connecting the line segments). We also performed this analysis for the video events at the hinge-point locations. Finally, we created word clouds by extracting the top 100 words and plotting them where the size of the word is proportional to its `activation' in the event.

>>>>

\subsubsection{Modeling verbal recall}
After watching the video, participants verbally recalled (in order) as much of the episode as they could.  We used the same topic model (fit with the text descriptions of the video) to transform participants' verbal recall transcripts. The result was a sentences (range: 68 to 294, mean: 131.94) by topics (100) matrix for each participant, where each row represents a probabalistic mixture of topics for a given window of sentences during recall. An example participant's (\#13) recall model is plotted in Fig.~\ref{fig:model}c. Like the video model, topic vectors were sparse and changed gradually.  Note that the topics were derived solely from the text descriptions of the video, and so the topic models estimated for recall are dependent on the topics present in the video. This approach effectively projects the participants' verbal recall into the video's `topic space'', allowing us to directly compare them to the video model.

@@

\begin{figure}[t!]
\centering
\includegraphics[width=1\textwidth]{figs/4_trajectory.pdf}
\caption{\small \textbf{Video and recall trajectory plots.} A). 2-dimensional embedding of the video events model. The arrows indicate the forward direction of the video events. B). 2-dimensional embedding of the average recall events model.  The colors refer to the most similar video events. The directional lines connecting the points represent the true video event order. The arrows represent the average direction of all recall event transitions (i.e. a line segment connecting two consecutive recall event vectors) that intersected a box (width=.25) centered on the origin of the arrow.}
\label{fig:trajectory}
\end{figure}

@@

\subsubsection{Topic vector word clouds}
 We created word clouds to visualize the themes contained in the ``hinge-point'' recall events of the model. One component of the topic model comprises a words (???) by topics (100) matrix (R), where the rows represent the weighting of a given word on each topic. Each event (video and recall) was associated with a 1 by 100 topic vector (v) representing the mixture of topics contained in the event. To find words associated with a given event, we computed the dot product between R and v, which gave a 1 by \# of words vector where the values represent the `activation' of each of in the event. We normalized these vectors by subtracting the average `activation' across all events. We performed this analysis for each of the line segment model `hinge-points' (i.e. the average recall events connecting the line segments). We also performed this analysis for the video events at the hinge-point locations. Finally, we created word clouds by extracting the top 100 words and plotting them where the size of the word is proportional to its `activation' in the event.
